---
geometry: margin=.4in
header-includes: \usepackage{tabularx} \usepackage{float} \usepackage{graphicx,colortbl,xcolor}\usepackage{mathptmx}
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F)
library(dplyr)
bold <- function(x) {return(paste0("\\textbf{",x,"}"))}
library(stringr)
library(tidyr)
library(knitr)# ; library(kableExtra)

```

\includegraphics{~/Desktop/PACE2017large.png}
\begin{center}
{\huge \textbf{Tournament Schedule}}
\end{center}

# Tournament Overview

## Friday, 9 June 2017
- 6:00 p.m. - 9:00 p.m.: Tea.m. Check-in (Hyatt Regency lobby level atrium)
- 7:00 p.m. - 9:00 p.m.: David Riley Coaches and Players Conference (Hartsfield)

## Saturday, 10 June 2017

- 7:00 a.m. -- 7:45 a.m.: Tea.m. Check-in for teams that arrive Saturday Morning (Hyatt Regency lobby level atrium)
- 8:00 a.m. -- 8:30 a.m.: Opening meeting (Rosemont Ballroom)
- 9:00 a.m. -- 1:00 p.m.: Preliminary Rounds (rounds 1--7)
- 1:00 p.m. -- 1:40 p.m.: Tiebreaker A
- 1:40 p.m. -- 3:00 p.m.: Lunch    
*Playoff seeds will be posted at ~2:30 p.m.*
- 3:00 p.m. -- 6:00 p.m.: Playoff rounds (rounds 8--12)
- 6:00 p.m. -- 6:30 p.m.: Tiebreaker B  
*Superplayoff and placement round seeds will be posted at ~8:00 p.m.*

## Sunday, 11 June 2017
- 8:15 a.m.: Teams report to Round 13 rooms
- 8:30 a.m. -- 10:15 a.m.: Placement rounds (for teams below Tier II and not involved in tier-crossing games)
- 8:30 a.m. -- 12:00 p.m.: Superplayoff rounds and Tier-crossing rounds (13--18)
- 11:00 a.m. -- 12:00 p.m.: Junior Varsity and Small School finals, as needed
- 12:00 p.m. -- 1:30 p.m.: Lunch    
*All times below are subject to slight (~15--30 min) changes, depending on the nature of ties that need to be broken*
- 1:30 p.m.: Tiebreaker C
- 2:15 p.m.: Tournament Finals (Rosemont Ballroom)
- 3:15 p.m.: All-Star Game (Rosemont Ballroom)
- 3:50 p.m.: Awards Ceremony (Rosemont Ballroom)
- 4:30 p.m.: Tournament ends

\clearpage

\setcounter{tocdepth}{2}
\tableofcontents{}

\clearpage

```{r "make prelim schedules", results = "asis", echo=FALSE }
library(knitr)
library(xtable)

s <- read.csv("~/nongrad/quizbowl/2017-pacensc/program/schedule/2017-pace-nsc-prelim-schedule.csv", header = F)
# prelim_brackets <- as.list(read.csv("~/nongrad/quizbowl/2017-pacensc/program/schedule/2017-pace-nsc-prelim-brackets.csv", stringsAsFactors = F))
prelim_brackets <- as.list(read.csv("~/nongrad/quizbowl/2017-pacensc/program/schedule/2017-pace-nsc-seeds-fri-morn.csv", stringsAsFactors = F))
prelim_bracket_names <- names(prelim_brackets)

### CHANGE ME!
bracket_room_list <- as.list(read.csv("~/nongrad/quizbowl/2017-pacensc/program/schedule/2017-pace-nsc-prelim-rooms.csv", stringsAsFactors = F, header = T))
# bracket_room_list <- list(maple = letters[1:4], oak = letters[1:4], birch = letters[1:4], willow = letters[1:4], cedar = letters[1:4],
                        # elm = letters[1:4], chestnut = letters[1:4], hemlock = letters[1:4], pine = letters[1:4], ash = letters[1:4],
                        # magnolia = letters[1:4], dogwood = letters[1:4])
s <- as.matrix(s)
# colnames(s)  <- NULL 

make_brackets_schedule <- function(s, which_bracket) {
  to_return <- s
  teamnames <- sort(which_bracket)

  for (ii in 1:8){
    to_return[which(to_return == ii)] <- teamnames[ii]
  }
  rownames(to_return) = paste("Round", 1:7)
  return(to_return)
}

prelim_bracket_schedules <- lapply(prelim_brackets, function(x) make_brackets_schedule(s, x))

prelim_printer <- function(bracket_name, bracket_sched, bracket_room_list) {
  addtorow <- list()
  addtorow$pos <- list(0,7)
  addtorow$command <- c(paste0("& \\multicolumn{2}{c|}{\\textbf{", bracket_room_list[1] ,"}} & \\multicolumn{2}{c|}{\\textbf{", bracket_room_list[2],"}} & \\multicolumn{2}{c|}{\\textbf{", bracket_room_list[3],"}} & \\multicolumn{2}{c|}{\\textbf{", bracket_room_list[4], "}}  \\\\\n"),
                        paste0("\\hline \\multicolumn{9}{|c|}{After Round 7, send one student to \\textbf{", bracket_room_list[1],"} to verify records and determine tiebreakers.}  \\\\\n"))
  xbracket_sched <- xtable(bracket_sched)
  align(xbracket_sched) <-"|l|XX|XX|XX|XX|"
  print(xbracket_sched, type = 'latex', add.to.row = addtorow, include.colnames = FALSE, comment=F, sanitize.colnames.function = bold, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H", size="\\footnotesize")
  cat(paste0("**Do not leave for lunch until you are dismissed by your bracket captain in  ", bracket_room_list[1], "** \n\n"))
}
```

# Stage 1: Prelims (Saturday before lunch)

## Team directory

```{r team-directory, results = 'asis', echo = F, warning = F}
prelim_brackets_df <- as.data.frame(prelim_brackets)
prelim_brackets_print <- read.csv("~/nongrad/quizbowl/2017-pacensc/program/schedule/2017-pace-nsc-seeds-for-directory-fri-morn.csv", stringsAsFactors = F)
team_dir <- reshape2::melt(prelim_brackets_print, measure.vars = 1:12)
colnames(team_dir) <- c("Bracket", "Team")
team_dir <- team_dir[order(team_dir$Team),]
team_dir <- team_dir %>% select(Team, Bracket)

team_dir_to_print <- team_dir[1:48,]
team_dir_to_print <- cbind(team_dir_to_print, team_dir[49:96,])

xteam_dir_to_print <- xtable(team_dir_to_print)
align(xteam_dir_to_print) <- "cll||ll"
print(xteam_dir_to_print, type = 'latex', include.rownames = FALSE, comment=F, table.placement = "H", sanitize.colnames.function = bold, size="\\small")
```

\clearpage

```{r "print prelim schedules" ,results = 'asis', echo = F}
for(ii in 1:12 ) {
  cat(paste("\n\n##", prelim_bracket_names[ii], "\n"))
  cat("### Teams:\n")
  aa <- matrix(sort(prelim_brackets_print[,ii]), nrow = 4)
  # colnames(aa) <- c("a", "b")
  print(kable((aa)))
  cat("### Schedule:\n")
  prelim_printer(names(bracket_room_list)[ii], prelim_bracket_schedules[[ii]], bracket_room_list[[ii]])
  # cat("blah lunch blah\n\n")
  cat("Minimatches will be played to break ties that affect which Playoff tier teams advance to. Playoff assignments will be posted	in several locations and to	the	PACE website by ~2:30pm.	Teams	are	expected to	be in	their	Round	8	room,	ready	to play, by	2:50pm.")
  
  if (ii %% 2 == 0) {  cat("\\clearpage")}
  if (ii %% 2 == 1) {  cat(paste(" \n \n \n \\rule{\\textwidth}{.4pt}"))}
  if (ii %% 2 == 1) {  cat(paste("  \\rule{\\textwidth}{.4pt} "))}
}
```














```{r, include = F}
# Make playoff schedules ----
s2 <- read.csv("~/nongrad/quizbowl/2017-pacensc/program/schedule/2017-pace-nsc-playoff-schedule.csv",header = F)
s2 <- as.matrix(s2)
colnames(s2)  <- NULL 
playoff_bracket_names <- c("Amazon" ,"Bramhaputra" ,"Congo" ,"Darling" ,"Euphrates" ,"Fly" ,"Ganges" ,"Harlem" ,"Irrawaddy" ,"Jordan" ,"Kaveri" ,"Loire" ,"Mississippi" ,"Nile" ,"Orinoco" ,"Pasig")

playoff_brackets <- lapply(1:16, function(x) paste0(LETTERS[x], 1:6))
names(playoff_brackets) <- paste0("Bracket", LETTERS[1:16])
playoff_rooms <- as.list(read.csv("~/nongrad/quizbowl/2017-pacensc/program/schedule/2017-pace-nsc-playoff-rooms.csv", stringsAsFactors = F))
make_payoff_schedules <- function(which_bracket){
  to_return <- s2
  for (ii in 1:6){
    to_return[which(to_return == ii)] <- which_bracket[ii]
  }
  return(to_return)
}

playoff_schedules <- lapply(playoff_brackets, function(x) make_payoff_schedules(x))

```


# Stage 2: Playoffs (Saturday after lunch)

```{r, results = "asis", echo = F}
# To print out the top half -------------


playoff_bracket_printer  <- function(which_set) {
  t1playoff_brackets_print <- matrix(paste0(rep(LETTERS[(1:4+which_set)], each = 6), 1:6,":\n\n"), nrow = 6, byrow = F)
  colnames(t1playoff_brackets_print) <- playoff_bracket_names[1:4+which_set]
  xt1playoff_brackets_print <- xtable(t1playoff_brackets_print)
  align(xt1playoff_brackets_print) <- "|c|X|X|X|X|"
  print(xt1playoff_brackets_print, type = 'latex', include.colnames = TRUE, sanitize.colnames.function = bold, comment=F, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H", hline.after = -1:6)

}

playoff_printer <- function(which_pair) {
  tab2print <- cbind(playoff_schedules[[which_pair]], playoff_schedules[[which_pair+1]])
  rownames(tab2print) <- paste("Round", 8:12)
  addtorow <- list()
  if (which_pair < 8) {
    addtorow$pos <- list(-1,0,5)
    addtorow$command <- c(paste0("\\hline & \\multicolumn{6}{c||}{\\textbf{", playoff_bracket_names[which_pair] ,"}} & \\multicolumn{6}{c|}{\\textbf{", playoff_bracket_names[which_pair+1] ,"}}  \\\\\n"), paste0("& \\multicolumn{2}{c|}{\\textbf{", playoff_rooms[[which_pair]][1]  ,"}} & \\multicolumn{2}{c|}{\\textbf{", playoff_rooms[[which_pair]][2] ,"}} & \\multicolumn{2}{c||}{\\textbf{", playoff_rooms[[which_pair]][3] ,"}} & \\multicolumn{2}{c|}{\\textbf{", playoff_rooms[[which_pair+1]][1] , "}} & \\multicolumn{2}{c|}{\\textbf{", playoff_rooms[[which_pair+1]][2] ,"}} & \\multicolumn{2}{c|}{\\textbf{",playoff_rooms[[which_pair+1]][3] ,"}}  \\\\\n"), paste0("\\hline & \\multicolumn{6}{c||}{\\footnotesize{Send one student to \\textbf{", playoff_rooms[[which_pair]][1] ,"} to verify records}} & \\multicolumn{6}{c|}{\\footnotesize{Send one student to \\textbf{", playoff_rooms[[which_pair+1]][1] ,"} to verify records}}  \\\\\n")) 
  }
  else {
    addtorow$pos <- list(-1,0, 5)
    addtorow$command <- c(paste0("\\hline & \\multicolumn{6}{c||}{\\textbf{", playoff_bracket_names[which_pair] ,"}} & \\multicolumn{6}{c|}{\\textbf{", playoff_bracket_names[which_pair+1] ,"}}  \\\\\n"), paste0("& \\multicolumn{2}{c|}{\\textbf{", playoff_rooms[[which_pair]][1]  ,"}} & \\multicolumn{2}{c|}{\\textbf{", playoff_rooms[[which_pair]][2] ,"}} & \\multicolumn{2}{c||}{\\textbf{", playoff_rooms[[which_pair]][3] ,"}} & \\multicolumn{2}{c|}{\\textbf{", playoff_rooms[[which_pair+1]][1] , "}} & \\multicolumn{2}{c|}{\\textbf{", playoff_rooms[[which_pair+1]][2] ,"}} & \\multicolumn{2}{c|}{\\textbf{",playoff_rooms[[which_pair+1]][3] ,"}}  \\\\\n"), paste0("\\hline \\multicolumn{13}{|c|}{\\small{\\textbf{Report your playoff record and a contact phone number to your Round 12 moderator for verification.}}}  \\\\\n")) 
  }
  xbracket_sched <- xtable(tab2print)
  align(xbracket_sched) <-"|r|XX|XX|XX||XX|XX|XX|"
  print(xbracket_sched, type = 'latex', add.to.row = addtorow, include.colnames = FALSE,  comment=F, sanitize.colnames.function = bold, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H")
}

cat("\n## Playoffs: Tier I\n")
playoff_bracket_printer(0)
playoff_printer(1)
playoff_printer(3)
cat("Ties to determine which Sunday bracket a team will advance to will be played off immediately on Saturday night. Playoff stats and Superplayoff	assignments	will	be	posted	to	the	PACE	website	and	HSQuizBowl.org approximately	one	hour	after	the	conclusion	of	Round	12.	\\textbf{Please	confirm	your	record	with the posted schedule.	If	there	is an	error,	please	email	tournament.director@pace-nsc.org	by	11:00pm	Saturday.	}")
cat("\\clearpage")

cat("\n\n## Playoffs: Tier II\n")
playoff_bracket_printer(4)
playoff_printer(5)
playoff_printer(7)
cat("In all Tier II brackets, ties to determine the first-place team will be played off immediately. All other ties will be broken by PPG. Playoff	stats	and	placement	round	assignments	will	be	posted	to	the	PACE	website	and	HSQuizBowl.org approximately	one	hour	after	the	conclusion	of	Round	12.	\\textbf{Please	confirm	your	record	Saturday	night.	If	there	is an	error,	please	email	tournament.director@pace-nsc.org	by	11:00pm	Saturday night.	}")
cat("\\clearpage")

cat("\n\n## Playoffs: Tier III\n")
playoff_bracket_printer(8)
playoff_printer(9)
playoff_printer(11)
cat("Playoff	stats	and	placement	round	assignments	will	be	posted	to	the	PACE	website	and	HSQuizBowl.org approximately	one	hour	after	the	conclusion	of	Round	12.	\\textbf{Please	confirm	your	record	Saturday	night.	If	there	is an	error,	please	email	tournament.director@pace-nsc.org	by	11:00pm	Saturday night.	}")
cat("\\clearpage")

cat("\n\n## Playoffs: Tier IV\n")
playoff_bracket_printer(12)
playoff_printer(13)
playoff_printer(15)
cat("Playoff	stats	and	placement	round	assignments	will	be	posted	to	the	PACE	website	and	HSQuizBowl.org approximately	one	hour	after	the	conclusion	of	Round	12.	\\textbf{Please	confirm	your	record	Saturday	night.	If	there	is an	error,	please	email	tournament.director@pace-nsc.org	by	11:00pm	Saturday night.	}")

```

\clearpage

# Stage 3: Superplayoffs & Placement Rounds (Sunday morning)



```{r, super, results = 'asis', echo = F}
cat("\n\n## Championship Superplayoffs: Competing for spots 1-8\n")
# superplayoff_brackets <- matrix(paste0(rep(LETTERS[1:4],2), rep(c(1,2), each = 4)), nrow = 2, byrow = T)



superplayoff_brackets <- as.matrix(read.csv("~/nongrad/quizbowl/2017-pacensc/during-nsc/top-sunday.csv", header = F, stringsAsFactors = F))

xt1superplayoff_brackets_print <- matrix(paste0(superplayoff_brackets, " "), nrow = 2)
xt1superplayoff_brackets_print <- xtable(xt1superplayoff_brackets_print)
align(xt1superplayoff_brackets_print) <- "|c|X|X|X|X|"
print(xt1superplayoff_brackets_print, type = 'latex', include.colnames = FALSE, include.rownames = FALSE, 
      comment=F, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H", hline.after = 0:2 )

champ_sched <- read.csv("~/Downloads/2017 PACE NSC tentative schedules - champ-superplayoff-sched.csv", header = F, stringsAsFactors = F)
rownames(champ_sched) <- paste("Round", 13:18)
### CHANGE ME!
superplayoff_rooms <- read.csv("~/nongrad/quizbowl/2017-pacensc/program/schedule/2017-pace-nsc-superplayoff-rooms.csv")
champ_rooms <- superplayoff_rooms[1:4,1]
xtchampsched <- xtable(champ_sched)
align(xtchampsched) <- "|c|XX|XX|XX|XX|"
  addtorow <- list()
  addtorow$pos <- list(0, 6)
  addtorow$command <- c(paste0("& \\multicolumn{2}{c|}{\\textbf{", champ_rooms[1] ,"}} & \\multicolumn{2}{c|}{\\textbf{", champ_rooms[2],"}} & \\multicolumn{2}{c|}{\\textbf{", champ_rooms[3],"}} & \\multicolumn{2}{c|}{\\textbf{", champ_rooms[4], "}}  \\\\\n"),
                        paste0("\\hline & \\multicolumn{8}{c|}{Send one student to \\textbf{", champ_rooms[1] ,"} to verify records and confirm afternoon schedule} \\\\\n"))

print(xtchampsched, type = 'latex', add.to.row = addtorow, include.colnames = FALSE, include.rownames = T, comment=F, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H")


```

### Procedure for determining placement in championship superplayoff bracket:

- If the first-place team has a lead of two or more games over second place, they will be declared champions without a final.
- If the first-place team has a lead of exactly one game, they will have the advantage in a two-game final. The leading team must win once; the trailing team must win both games. If there is a tie for second, there will be a tiebreaker to determine the second team in the final.
- If the top two teams are tied, there will be a one-game final. If more than two teams are tied for first, they will be seeded into a single-elimination bracket.

- Teams that are tied in the standings that are not in contention will play tiebreaker games to determine their final rank. In the case of a two-way tie, a full game will be used. In the case of a larger tie, a series of minimatches will be used. Any team which declines to play a tiebreaker game will be considered to forfeit the tiebreaker and be ranked below teams that wish to play.

- **All tiebreaker games will be played *after lunch* on Sunday**


\newpage

```{r, spot916, results = 'asis', echo = F}
cat("\n\n## Superplayoffs: Competing for spots 9-16\n")
# superplayoff_brackets <- matrix(paste0(rep(LETTERS[1:4],2), rep(c(3,4), each = 4)), nrow = 2, byrow = T)
superplayoff_brackets <- as.matrix(read.csv("~/nongrad/quizbowl/2017-pacensc/during-nsc/second-sunday.csv", header = F, stringsAsFactors = F))

xt1superplayoff_brackets_print <- matrix(paste0(superplayoff_brackets, ""), nrow = 2)
xt1superplayoff_brackets_print <- xtable(xt1superplayoff_brackets_print)
align(xt1superplayoff_brackets_print) <- "|c|X|X|X|X|"
print(xt1superplayoff_brackets_print, type = 'latex', include.colnames = FALSE, include.rownames = FALSE, 
      comment=F, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H", hline.after = 0:2 )


p916_sched <- apply(champ_sched, 1, function(x) stringr::str_replace(x, "1", "3"))
p916_sched <- apply(p916_sched, 1, function(x) stringr::str_replace(x, "2", "4"))
rownames(p916_sched) <- paste("Round", 13:18)

### CHANGE ME!
p916_rooms <- superplayoff_rooms[5:8, 1]
xtp916sched <- xtable(p916_sched)
align(xtp916sched) <- "|c|XX|XX|XX|XX|"
addtorow <- list()
addtorow$pos <- list(0, 6)
addtorow$command <- c(paste0("& \\multicolumn{2}{c|}{\\textbf{", p916_rooms[1] ,"}} & \\multicolumn{2}{c|}{\\textbf{", p916_rooms[2],"}} & \\multicolumn{2}{c|}{\\textbf{", p916_rooms[3],"}} & \\multicolumn{2}{c|}{\\textbf{", p916_rooms[4], "}}  \\\\\n"),
                      paste0("\\hline & \\multicolumn{8}{c|}{Send one student to \\textbf{", p916_rooms[1] ,"} to verify records} \\\\\n"))

print(xtp916sched, type = 'latex', add.to.row = addtorow, include.colnames = FALSE, include.rownames = T, comment=F, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H")
```

### Procedure for determining placement in 9-16 superplayoff bracket:
- Teams that are tied in the standings will play tiebreaker games to determine their final rank. 
- In the case of a two-way tie, a full game will be used. In the case of a larger tie, a series of minimatches will be used. Any team which declines to play a tiebreaker game will be considered to forfeit the tiebreaker and be ranked below teams that wish to play.
- **All tiebreaker games will be played *after lunch* on Sunday**

\newpage

```{r, spot1728, results = 'asis', echo = F}
cat("\n\n## Superplayoffs: Competing for spots 17-28\n")
# superplayoff_brackets <- matrix(paste0(rep(LETTERS[1:4],2), rep(c(5,6), each = 4)), nrow = 2, byrow = T)
# superplayoff_brackets <- rbind(superplayoff_brackets, c("E1", "G1", "F1", "H1"))

superplayoff_brackets <- as.matrix(read.csv("~/nongrad/quizbowl/2017-pacensc/during-nsc/third-sunday.csv", header = F, stringsAsFactors = F))

xt1superplayoff_brackets_print <- matrix(paste0(superplayoff_brackets, ""), nrow = 3)
xt1superplayoff_brackets_print <- xtable(xt1superplayoff_brackets_print)
align(xt1superplayoff_brackets_print) <- "|c|X|X|X|X|"
print(xt1superplayoff_brackets_print, type = 'latex', include.colnames = FALSE, include.rownames = FALSE, 
      comment=F, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H", hline.after = 0:3)

p1728_sched <- read.csv("~/nongrad/quizbowl/2017-pacensc/program/schedule/2017-pace-nsc-crossover-schedule.csv", header = F, stringsAsFactors = F)

rownames(p1728_sched) <- paste("Round", 13:17)
xtp1728_sched <- xtable(p1728_sched)
align(xtp1728_sched) <- "|c|XX|XX|XX||XX|XX|XX|"
p1728_rooms <- superplayoff_rooms[9:14,1]

addtorow <- list()
addtorow$pos <- list(-1, 0, 5)
addtorow$command <- c("\\hline & \\multicolumn{6}{c||}{\\textbf{Hood}} & \\multicolumn{6}{c|}{\\textbf{Rainier}} \\\\\n",paste0("& \\multicolumn{2}{c|}{\\textbf{", p1728_rooms[1] ,"}} & \\multicolumn{2}{c|}{\\textbf{", p1728_rooms[2],"}} & \\multicolumn{2}{c||}{\\textbf{", p1728_rooms[3],"}} & \\multicolumn{2}{c|}{\\textbf{", p1728_rooms[4] ,"}} & \\multicolumn{2}{c|}{\\textbf{", p1728_rooms[5],"}} & \\multicolumn{2}{c|}{\\textbf{", p1728_rooms[6],"}} \\\\\n"),
                        paste0("\\hline & \\multicolumn{12}{c|}{Send one student to \\textbf{", p1728_rooms[1] ,"} to verify records and confirm Round 18 schedule}  \\\\\n"))

print(xtp1728_sched, type = 'latex', add.to.row = addtorow, include.colnames = FALSE, include.rownames = T, comment=F, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H")


```

**After Round 17**, teams in the Rainier and Hood brackets will be ranked 1-6, by record and PPG. During Round 18, each team will play a single game against the team with the same rank from the opposite bracket. For instance, the third place teams will play for 21st place. **These games will take place before lunch on Sunday**.

```{r results = "asis", echo = F}
p1728_final_bracket <- matrix(paste0(rep(c("H", "R"), each = 6), 1:6, ":\n\n\n"), nrow = 2, byrow = T)
xp1728_final_bracket <- xtable(p1728_final_bracket)
align(xp1728_final_bracket) <- "|c|X|X|X|X|X|X|"

print(xp1728_final_bracket, type = 'latex', include.colnames = FALSE, include.rownames = FALSE, 
      comment=F, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H", hline.after = 0:2)

p1728_final_sched <- matrix(paste0(rep(c("H", "R"), times = 6), rep(1:6, each = 2)), nrow = 1)
rownames(p1728_final_sched) <- "Round 18"
xp1728_final_sched <- xtable(p1728_final_sched)
align(xp1728_final_sched) <- "|c|XX|XX|XX|XX|XX|XX|"
addtorow <- list()
addtorow$pos <- list(-1, 0)
addtorow$command <- c(paste0("\\hline \\multicolumn{1}{|c|}{competing for}& \\multicolumn{2}{c}{17th Place} & \\multicolumn{2}{|c}{19th place} & \\multicolumn{2}{|c|}{21st place} & \\multicolumn{2}{c|}{23rd place} & \\multicolumn{2}{c|}{25th place} & \\multicolumn{2}{c|}{27th place} \\\\\n"), paste0("& \\multicolumn{2}{c}{\\textbf{", p1728_rooms[1] ,"}} & \\multicolumn{2}{|c}{\\textbf{", p1728_rooms[2],"}} & \\multicolumn{2}{|c|}{\\textbf{", p1728_rooms[3],"}} & \\multicolumn{2}{c|}{\\textbf{", p1728_rooms[4] ,"}} & \\multicolumn{2}{c|}{\\textbf{", p1728_rooms[5],"}} & \\multicolumn{2}{c|}{\\textbf{", p1728_rooms[6],"}} \\\\\n"))

print(xp1728_final_sched, type = 'latex', add.to.row = addtorow, include.colnames = FALSE, include.rownames = T, comment=F, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H")

```
 
\newpage

## Placement rounds: Competing for spots 29-96 (Tiers II, III, IV)

```{r, placement, results = 'asis', echo = F}

placement_games <- read.csv("~/nongrad/quizbowl/2017-pacensc/program/schedule/2017-pace-nsc-placement-schedule.csv", header = F, stringsAsFactors = F)

p2948 <- placement_games[1:3,5:24]
rownames(p2948) <- paste("R", 13:15)
p2948_rooms <- superplayoff_rooms[15:24,1]
colnames(p2948) <- p2948_rooms
p4971 <- placement_games[4:6,]
rownames(p4971) <- paste("R", 13:15)
p4971_rooms <- superplayoff_rooms[25:36,1]
p7296 <- placement_games[7:9,]
rownames(p7296) <- paste("R", 13:15)
p7296_rooms <- superplayoff_rooms[37:48,1]


print_placement_schedule <- function(which_bracket, rooms) {
  xwhich_bracket <- xtable(which_bracket)
  align_by <- capture.output(cat('|l', rep("|XX", ncol(which_bracket)/2), '|', sep = ""))
  align(xwhich_bracket) <- align_by
  
  
  addtorow$pos <- list(0)
  addtorow$command <- capture.output(cat("\\hline ", paste0("& \\multicolumn{2}{p{1cm}|}{\\footnotesize{", rooms ,"}}"), "\\\\\n"))
  
  
  print(xwhich_bracket, type = 'latex', include.colnames = FALSE, include.rownames = TRUE, 
        comment=F, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H", hline.after = 0:3, add.to.row = addtorow, sanitize.colnames.function = bold)
}

cat("\\textbf{Tier II}")

# pp <- matrix(paste0(LETTERS[5:8], rep(2:6, each = 4), ":\n\n\n"), nrow = 4)
pp <- t(read.csv("~/nongrad/quizbowl/2017-pacensc/during-nsc/tier-ii-placement-games.csv", header = F, stringsAsFactors = F))
rownames(pp) <- NULL
xtpp <- xtable(pp)
align(xtpp) <-"|l|X|X|X|X|X|"
addtorow$pos <- list(0)
addtorow$command <- paste0(" & 29th Place & 33rd Place & 37th Place & 41st Place & 45th place \\\\\n")
  
print(xtpp,  type = 'latex', include.colnames = FALSE, 
        comment=F, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H", add.to.row = addtorow, sanitize.colnames.function = bold)

print_placement_schedule(which_bracket = p2948, p2948_rooms)




cat("\\textbf{Tier III}")

# cat("\n\n### Tier III placement rounds\n")
# pp <- matrix(paste0(LETTERS[9:12], rep(1:6, each = 4), ":\n\n\n"), nrow = 4)
pp <- t(read.csv("~/nongrad/quizbowl/2017-pacensc/during-nsc/tier-iii-placement-games.csv", header = F, stringsAsFactors = F))

xtpp <- xtable(pp)
align(xtpp) <-"|l|X|X|X|X|X|X|"
addtorow$pos <- list(0)
addtorow$command <- paste0("& 49th Place & 53rd Place & 57th Place & 61st Place & 65th place & 69th place \\\\\n")
print(xtpp,  type = 'latex', include.colnames = FALSE, include.rownames = TRUE, 
        comment=F, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H", add.to.row = addtorow, sanitize.colnames.function = bold)

print_placement_schedule(which_bracket = p4971, p4971_rooms)



cat("\\textbf{Tier IV}")
# cat("\\rule{\\textwidth}{1pt}")
# cat("\n\n### Tier IV placement rounds\n")
# pp <- matrix(paste0(LETTERS[13:16], rep(1:6, each = 4), ":\n\n\n"), nrow = 4)
pp <- t(read.csv("~/nongrad/quizbowl/2017-pacensc/during-nsc/tier-iv-placement-games.csv", header = F, stringsAsFactors = F))

xtpp <- xtable(pp)
align(xtpp) <-"|l|X|X|X|X|X|X|"
addtorow$pos <- list(0)
addtorow$command <- paste0("& 73rd Place & 77th Place & 81st Place & 85th Place & 89th place & 93rd place \\\\\n")
print(xtpp,  type = 'latex', include.colnames = FALSE, include.rownames = TRUE, 
        comment=F, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H", add.to.row = addtorow)
print_placement_schedule(which_bracket = p7296, p7296_rooms)

```

\clearpage

## Procedure for determining Small School/JV Champions

- Any SS/JV team that finishes alone in the following three brackets (Championship superplayoffs; 9-16 Superplayoffs; 17-28 Crossover bracket) will automatically be awarded the SS/JV title. 
- If multiple teams with SS/JV status reach the top 28, the team's final standings will be used to determine SS/JV standings (e.g. if SS School 1 finishes the tournament as the 8th place team and SS School 2 as 11th place team, then SS School 1 is the top Small School at NSC)

- If no SS/JV team teams finish in the top 28, then a final will be held for first place **if the second-highest team is within *eight* places of the highest team** after Round 15.
- **After Round 15**, SS/JV teams that finish outside of the top 28 should send one team representative to **Sky Harbor A** to confirm whether they need to compete in SS/JV finals.