---
geometry: margin=.5in
header-includes: \usepackage{tabularx} \usepackage{float} \usepackage{graphicx,colortbl,xcolor}
output:
  pdf_document: default
  word_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\includegraphics{~/Desktop/PACE2017large.png}
\begin{center}
{\huge \textbf{2017 PACE NSC Tournament Schedule}}
\end{center}

# Tournament Schedule

### Friday, 9 June 2017
- 6:00 - 9:00 PM: Team Check-in 
- 7:00 - 9:00 PM: David Riley Coaches Conference (*timing tentative; final time will be announced on hsquizbowl.org*)

### Saturday, 10 June 2017

- 7:00 - 7:45 AM: Team Check-in for teams that arrive Saturday Morning
- 8:00 - 8:30 AM: Opening meeting (Rosemont Ballroom)
- 9:00 AM - 1:00 PM: Preliminary Rounds (rounds 1-7)
- 1:00 - 1:40 PM: Tiebreaker A
- 1:40 - 3:00 PM: Lunch    
*Playoff seeds will be posted at ~2:30 PM*
- 3:00 - 6:00 PM: Playoff rounds (rounds 8-12)
- 6:00 - 6:30 PM: Tiebreaker B  
*Superplayoff and placement round seeds will be posted at ~8:00 pm*

### Sunday, 11 June 2017
- 8:15 AM: Teams report to Round 13 rooms
- 8:30 AM - 10:15 AM: Placement rounds (for teams below Tier II and not involved in tier-crossing games)
- 8:30 AM - 12:00 PM: Superplayoff rounds and Tier-crossing rounds (13-18)
- 11:00 AM - 12:00 PM: Junior Varsity and Small School finals, as needed
- 12:00 - 1:30 PM: Lunch    
*All times below are subject to slight (~15-30 min) changes, depending on the nature of ties that need to be broken*
- 1:30 PM: Tiebreaker C
- 2:15 PM: Tournament Finals
- 3:15 PM: All-Star Game
- 3:50 PM: Awards Ceremony
- 4:30 PM: Tournament ends

\clearpage

\setcounter{tocdepth}{2}
\tableofcontents{}

\clearpage

```{r "make prelim schedules", results = "asis", echo=FALSE }
library(knitr)
library(xtable)

s <- read.csv("~/nongrad/quizbowl/2017-pacensc/program/schedule/2017-pace-nsc-prelim-schedule.csv", header = F)
prelim_brackets <- as.list(read.csv("~/nongrad/quizbowl/2017-pacensc/program/schedule/2017-pace-nsc-prelim-brackets.csv", stringsAsFactors = F))
prelim_bracket_names <- names(prelim_brackets)

### CHANGE ME!
bracket_room_list <- as.list(read.csv("~/nongrad/quizbowl/2017-pacensc/program/schedule/2017-pace-nsc-prelim-rooms.csv", stringsAsFactors = F, header = T))
# bracket_room_list <- list(maple = letters[1:4], oak = letters[1:4], birch = letters[1:4], willow = letters[1:4], cedar = letters[1:4],
# elm = letters[1:4], chestnut = letters[1:4], hemlock = letters[1:4], pine = letters[1:4], ash = letters[1:4],
# magnolia = letters[1:4], dogwood = letters[1:4])
s <- as.matrix(s)
# colnames(s)  <- NULL 

make_brackets_schedule <- function(s, which_bracket) {
  to_return <- s
  for (ii in 1:8){
    to_return[which(to_return == ii)] <- which_bracket[ii]
  }
  rownames(to_return) = paste("Round", 1:7)
  return(to_return)
}

prelim_bracket_schedules <- lapply(prelim_brackets, function(x) make_brackets_schedule(s, x))

prelim_printer <- function(bracket_name, bracket_sched, bracket_room_list) {
  addtorow <- list()
  addtorow$pos <- list(0,7)
  addtorow$command <- c(paste0("& \\multicolumn{2}{c}{\\textbf{", bracket_room_list[1] ,"}} & \\multicolumn{2}{|c}{\\textbf{", bracket_room_list[2],"}} & \\multicolumn{2}{|c}{\\textbf{", bracket_room_list[3],"}} & \\multicolumn{2}{|c|}{\\textbf{", bracket_room_list[4], "}}  \\\\\n"),
                        paste0("\\hline \\multicolumn{9}{|c|}{After Round 7, send one student to room \\textbf{", bracket_room_list[1],"} to verify records.}  \\\\\n"))
  xbracket_sched <- xtable(bracket_sched)
  align(xbracket_sched) <-"|r|XX|XX|XX|XX|"
  print(xbracket_sched, type = 'latex', add.to.row = addtorow, include.colnames = FALSE, comment=F, sanitize.colnames.function = bold, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H")
}
```

# Stage 1: Prelims (Saturday before lunch)

```{r "print prelim schedules" ,results = 'asis', echo = F}
for(ii in 1:12 ) {
  cat(paste("\n\n##", prelim_bracket_names[ii], "\n"))
  cat("### Teams:\n")
  aa <- matrix(sort(prelim_bracket_schedules[[ii]][1,]))
  print(kable(t(aa)))
  cat("### Schedule:\n")
  prelim_printer(names(bracket_room_list)[ii], prelim_bracket_schedules[[ii]], bracket_room_list[[ii]])
  cat("Playoff assignments will be posted	in several locations and to	the	PACE website by 2:30pm.	Teams	are	expected to	be in	their	Round	8	room,	ready	to play, by	2:50pm.	These	times	are	subject	to change.")
  
  if (ii %% 2 == 0) {  cat("\\clearpage")}
  if (ii %% 2 == 1) {  cat(paste(" \n \n \n \\rule{\\textwidth}{.4pt}"))}
  if (ii %% 2 == 1) {  cat(paste("  \\rule{\\textwidth}{.4pt} "))}
  
}
```














```{r, include = F}
# Make playoff schedules ----
s2 <- read.csv("~/nongrad/quizbowl/2017-pacensc/program/schedule/2017-pace-nsc-playoff-schedule.csv",header = F)
s2 <- as.matrix(s2)
colnames(s2)  <- NULL 
playoff_bracket_names <- c("Amazon" ,"Bramhaputra" ,"Congo" ,"Darling" ,"Euphrates" ,"Fly" ,"Ganges" ,"Harlem" ,"Irrawaddy" ,"Jordan" ,"Kaveri" ,"Loire" ,"Mississippi" ,"Nile" ,"Orinoco" ,"Pasig")

playoff_brackets <- lapply(1:16, function(x) paste0(LETTERS[x], 1:6))
names(playoff_brackets) <- paste0("Bracket", LETTERS[1:16])
playoff_rooms <- as.list(read.csv("~/nongrad/quizbowl/2017-pacensc/program/schedule/2017-pace-nsc-playoff-rooms.csv", stringsAsFactors = F))
make_payoff_schedules <- function(which_bracket){
  to_return <- s2
  for (ii in 1:6){
    to_return[which(to_return == ii)] <- which_bracket[ii]
  }
  return(to_return)
}

playoff_schedules <- lapply(playoff_brackets, function(x) make_payoff_schedules(x))

```


# Stage 2: Playoffs (Saturday after lunch)

```{r, results = "asis", echo = F}
# To print out the top half -------------


playoff_bracket_printer  <- function(which_set) {
  t1playoff_brackets_print <- matrix(paste0(rep(LETTERS[(1:4+which_set)], each = 6), 1:6,":\n\n"), nrow = 6, byrow = F)
  colnames(t1playoff_brackets_print) <- playoff_bracket_names[1:4+which_set]
  xt1playoff_brackets_print <- xtable(t1playoff_brackets_print)
  align(xt1playoff_brackets_print) <- "|c|X|X|X|X|"
  print(xt1playoff_brackets_print, type = 'latex', include.colnames = TRUE, comment=F, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H", hline.after = -1:6)
  
}

playoff_printer <- function(which_pair) {
  tab2print <- cbind(playoff_schedules[[which_pair]], playoff_schedules[[which_pair+1]])
  rownames(tab2print) <- paste("Round", 8:12)
  addtorow <- list()
  addtorow$pos <- list(-1,0,5)
  addtorow$command <- c(paste0("\\hline & \\multicolumn{6}{c||}{\\textbf{", playoff_bracket_names[which_pair] ,"}} & \\multicolumn{6}{c|}{\\textbf{", playoff_bracket_names[which_pair+1] ,"}}  \\\\\n"), paste0("& \\multicolumn{2}{c|}{\\textbf{", playoff_rooms[[which_pair]][1]  ,"}} & \\multicolumn{2}{c|}{\\textbf{", playoff_rooms[[which_pair]][2] ,"}} & \\multicolumn{2}{c||}{\\textbf{", playoff_rooms[[which_pair]][2] ,"}} & \\multicolumn{2}{c|}{\\textbf{", playoff_rooms[[which_pair+1]][1] , "}} & \\multicolumn{2}{c|}{\\textbf{", playoff_rooms[[which_pair+1]][2] ,"}} & \\multicolumn{2}{c|}{\\textbf{",playoff_rooms[[which_pair+1]][3] ,"}}  \\\\\n"), paste0("\\hline & \\multicolumn{6}{c||}{\\footnotesize{Send one student to \\textbf{", playoff_rooms[[which_pair]][1] ,"} to verify records}} & \\multicolumn{6}{c|}{\\footnotesize{Send one student to \\textbf{", playoff_rooms[[which_pair+1]][1] ,"} to verify records}}  \\\\\n"))
  xbracket_sched <- xtable(tab2print)
  align(xbracket_sched) <-"|r|XX|XX|XX||XX|XX|XX|"
  print(xbracket_sched, type = 'latex', add.to.row = addtorow, include.colnames = FALSE, comment=F, sanitize.colnames.function = bold, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H")
}

cat("\n## Playoffs: Tier I\n")
playoff_bracket_printer(0)
playoff_printer(1)
playoff_printer(3)
cat("Playoff	stats	and	placement	round	assignments	will	be	posted	to	the	PACE	website	and	HSQuizBowl.org approximately	one	hour	after	the	conclusion	of	Round	12.	\\textbf{Please	confirm	your	record	Saturday	night.	If	there	is an	error,	please	email	tournament.director@pace-nsc.org	by	11:00pm	Saturday night.	}")
cat("\\clearpage")

cat("\n\n## Playoffs: Tier II\n")
playoff_bracket_printer(4)
playoff_printer(5)
playoff_printer(7)
cat("Playoff	stats	and	placement	round	assignments	will	be	posted	to	the	PACE	website	and	HSQuizBowl.org approximately	one	hour	after	the	conclusion	of	Round	12.	\\textbf{Please	confirm	your	record	Saturday	night.	If	there	is an	error,	please	email	tournament.director@pace-nsc.org	by	11:00pm	Saturday night.	}")
cat("\\clearpage")

cat("\n\n## Playoffs: Tier III\n")
playoff_bracket_printer(8)
playoff_printer(9)
playoff_printer(11)
cat("Playoff	stats	and	placement	round	assignments	will	be	posted	to	the	PACE	website	and	HSQuizBowl.org approximately	one	hour	after	the	conclusion	of	Round	12.	\\textbf{Please	confirm	your	record	Saturday	night.	If	there	is an	error,	please	email	tournament.director@pace-nsc.org	by	11:00pm	Saturday night.	}")
cat("\\clearpage")

cat("\n\n## Playoffs: Tier IV\n")
playoff_bracket_printer(12)
playoff_printer(13)
playoff_printer(15)
cat("Playoff	stats	and	placement	round	assignments	will	be	posted	to	the	PACE	website	and	HSQuizBowl.org approximately	one	hour	after	the	conclusion	of	Round	12.	\\textbf{Please	confirm	your	record	Saturday	night.	If	there	is an	error,	please	email	tournament.director@pace-nsc.org	by	11:00pm	Saturday night.	}")

```

\clearpage

# Stage 3: Superplayoffs & Placement Rounds (Sunday morning)



```{r, super, results = 'asis', echo = F}
cat("\n\n## Championship Superplayoffs: Competing for spots 1-8\n")
superplayoff_brackets <- matrix(paste0(rep(LETTERS[1:4],2), rep(c(1,2), each = 4)), nrow = 2, byrow = T)
xt1superplayoff_brackets_print <- matrix(paste0(superplayoff_brackets, ":\n\n\n"), nrow = 2)
xt1superplayoff_brackets_print <- xtable(xt1superplayoff_brackets_print)
align(xt1superplayoff_brackets_print) <- "|c|X|X|X|X|"
print(xt1superplayoff_brackets_print, type = 'latex', include.colnames = FALSE, include.rownames = FALSE, 
      comment=F, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H", hline.after = 0:2 )

champ_sched <- read.csv("~/Downloads/2017 PACE NSC tentative schedules - champ-superplayoff-sched.csv", header = F, stringsAsFactors = F)
rownames(champ_sched) <- paste("Round", 13:18)
### CHANGE ME!
champ_rooms <- paste0("ChampRoom", 1:4)
xtchampsched <- xtable(champ_sched)
align(xtchampsched) <- "|c|XX|XX|XX|XX|"
addtorow <- list()
addtorow$pos <- list(0, 6)
addtorow$command <- c(paste0("& \\multicolumn{2}{c}{\\textbf{", champ_rooms[1] ,"}} & \\multicolumn{2}{|c}{\\textbf{", champ_rooms[2],"}} & \\multicolumn{2}{|c}{\\textbf{", champ_rooms[3],"}} & \\multicolumn{2}{|c|}{\\textbf{", champ_rooms[4], "}}  \\\\\n"),
                      paste0("\\hline & \\multicolumn{8}{c|}{\\textbf{Send one student to ", champ_rooms[1] ," to verify records}} \\\\\n"))

print(xtchampsched, type = 'latex', add.to.row = addtorow, include.colnames = FALSE, include.rownames = T, comment=F, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H")
```

\newpage

```{r, spot916, results = 'asis', echo = F}
cat("\n\n## Superplayoffs: Competing for spots 9-16\n")
superplayoff_brackets <- matrix(paste0(rep(LETTERS[1:4],2), rep(c(3,4), each = 4)), nrow = 2, byrow = T)
xt1superplayoff_brackets_print <- matrix(paste0(superplayoff_brackets, ":\n\n\n"), nrow = 2)
xt1superplayoff_brackets_print <- xtable(xt1superplayoff_brackets_print)
align(xt1superplayoff_brackets_print) <- "|c|X|X|X|X|"
print(xt1superplayoff_brackets_print, type = 'latex', include.colnames = FALSE, include.rownames = FALSE, 
      comment=F, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H", hline.after = 0:2 )


p916_sched <- apply(champ_sched, 1, function(x) stringr::str_replace(x, "1", "3"))
p916_sched <- apply(p916_sched, 1, function(x) stringr::str_replace(x, "2", "4"))

### CHANGE ME!
p916_rooms <- paste0("P916", 1:4)
xtp916sched <- xtable(p916_sched)
align(xtp916sched) <- "|c|XX|XX|XX|XX|"
addtorow <- list()
addtorow$pos <- list(0, 6)
addtorow$command <- c(paste0("& \\multicolumn{2}{c}{\\textbf{", p916_rooms[1] ,"}} & \\multicolumn{2}{|c}{\\textbf{", p916_rooms[2],"}} & \\multicolumn{2}{|c}{\\textbf{", p916_rooms[3],"}} & \\multicolumn{2}{|c|}{\\textbf{", p916_rooms[4], "}}  \\\\\n"),
                      paste0("\\hline & \\multicolumn{8}{c|}{\\textbf{Send one student to ", p916_rooms[1] ," to verify records}} \\\\\n"))

print(xtchampsched, type = 'latex', add.to.row = addtorow, include.colnames = FALSE, include.rownames = T, comment=F, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H")
```


\newpage

```{r, spot1728, results = 'asis', echo = F}
cat("\n\n## Superplayoffs: Competing for spots 17-28\n")
superplayoff_brackets <- matrix(paste0(rep(LETTERS[1:4],2), rep(c(5,6), each = 4)), nrow = 2, byrow = T)
superplayoff_brackets <- rbind(superplayoff_brackets, c("E1", "G1", "F1", "H1"))
xt1superplayoff_brackets_print <- matrix(paste0(superplayoff_brackets, ":\n\n\n"), nrow = 3)
xt1superplayoff_brackets_print <- xtable(xt1superplayoff_brackets_print)
align(xt1superplayoff_brackets_print) <- "|c|X|X|X|X|"
print(xt1superplayoff_brackets_print, type = 'latex', include.colnames = FALSE, include.rownames = FALSE, 
      comment=F, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H", hline.after = 0:3)

p1728_sched <- read.csv("~/nongrad/quizbowl/2017-pacensc/program/schedule/2017-pace-nsc-crossover-schedule.csv", header = F, stringsAsFactors = F)

rownames(p1728_sched) <- paste("Round", 13:17)
xtp1728_sched <- xtable(p1728_sched)
align(xtp1728_sched) <- "|c|XX|XX|XX||XX|XX|XX|"
p1728_rooms <- paste0("P1728.r", 1:6)

addtorow <- list()
addtorow$pos <- list(-1, 0, 5)
addtorow$command <- c("\\hline & \\multicolumn{6}{c||}{\\textbf{Hood}} & \\multicolumn{6}{c|}{\\textbf{Ranier}} \\\\\n",paste0("& \\multicolumn{2}{c}{\\textbf{", p1728_rooms[1] ,"}} & \\multicolumn{2}{|c}{\\textbf{", p1728_rooms[2],"}} & \\multicolumn{2}{|c||}{\\textbf{", p1728_rooms[3],"}} & \\multicolumn{2}{c}{\\textbf{", p1728_rooms[4] ,"}} & \\multicolumn{2}{|c}{\\textbf{", p1728_rooms[5],"}} & \\multicolumn{2}{|c|}{\\textbf{", p1728_rooms[6],"}} \\\\\n"),
                      paste0("\\hline & \\multicolumn{12}{c|}{Send one student to ", p1728_rooms[1] ," to verify records}  \\\\\n"))

print(xtp1728_sched, type = 'latex', add.to.row = addtorow, include.colnames = FALSE, include.rownames = T, comment=F, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H")


```

**After Round 17**, teams will be ranked as 1-6 within the Ranier and Hood brackets. Each team will play a single game against the equally ranked group in the mirror bracket (e.g. H3 (the third place team in Hood) will play a game against R3 for 21st place)

```{r results = "asis", echo = F}
p1728_final_bracket <- matrix(paste0(rep(c("H", "R"), each = 6), 1:6, ":\n\n\n"), nrow = 2, byrow = T)
xp1728_final_bracket <- xtable(p1728_final_bracket)
align(xp1728_final_bracket) <- "|c|X|X|X|X|X|X|"

print(xp1728_final_bracket, type = 'latex', include.colnames = FALSE, include.rownames = FALSE, 
      comment=F, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H", hline.after = 0:2)

p1728_final_sched <- matrix(paste0(rep(c("H", "R"), times = 6), rep(1:6, each = 2)), nrow = 1)
rownames(p1728_final_sched) <- "Round 18"
xp1728_final_sched <- xtable(p1728_final_sched)
align(xp1728_final_sched) <- "|c|XX|XX|XX|XX|XX|XX|"
addtorow <- list()
addtorow$pos <- list(-1, 0)
addtorow$command <- c(paste0("\\hline \\multicolumn{1}{|c|}{competing for}& \\multicolumn{2}{c}{17th Place} & \\multicolumn{2}{|c}{19th place} & \\multicolumn{2}{|c|}{21st place} & \\multicolumn{2}{c|}{23rd place} & \\multicolumn{2}{c|}{25th place} & \\multicolumn{2}{c|}{27th place} \\\\\n"), paste0("& \\multicolumn{2}{c}{\\textbf{", p1728_rooms[1] ,"}} & \\multicolumn{2}{|c}{\\textbf{", p1728_rooms[2],"}} & \\multicolumn{2}{|c|}{\\textbf{", p1728_rooms[3],"}} & \\multicolumn{2}{c|}{\\textbf{", p1728_rooms[4] ,"}} & \\multicolumn{2}{c|}{\\textbf{", p1728_rooms[5],"}} & \\multicolumn{2}{c|}{\\textbf{", p1728_rooms[6],"}} \\\\\n"))

print(xp1728_final_sched, type = 'latex', add.to.row = addtorow, include.colnames = FALSE, include.rownames = T, comment=F, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H")

```

\newpage
## Placement Rounds

```{r, placement, results = 'asis', echo = F}

placement_games <- read.csv("~/nongrad/quizbowl/2017-pacensc/program/schedule/2017-pace-nsc-placement-schedule.csv", header = F, stringsAsFactors = F)

p2948 <- placement_games[1:3,5:20]
rownames(p2948) <- paste("R", 13:15)
p2948_rooms <- paste0("p2948.", 1:8)
p4971 <- placement_games[4:6,5:20]
rownames(p4971) <- paste("R", 13:15)
p4971_rooms <- paste0("p4971.", 1:8)
p7296 <- placement_games[7:9,5:24]
rownames(p7296) <- paste("R", 13:15)
p7296_rooms <- paste0("p7296.", 1:10)


print_placement_schedule <- function(which_bracket, rooms) {
  xwhich_bracket <- xtable(which_bracket)
  align_by <- capture.output(cat('|l', rep("|XX", ncol(which_bracket)/2), '|', sep = ""))
  align(xwhich_bracket) <- align_by
  
  
  addtorow$pos <- list(0)
  addtorow$command <- capture.output(cat("\\hline ", paste0("& \\multicolumn{2}{c|}{\\footnotesize{", rooms ,"}}"), "\\\\\n"))
  
  
  print(xwhich_bracket, type = 'latex', include.colnames = FALSE, include.rownames = TRUE, 
        comment=F, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H", hline.after = 0:3, add.to.row = addtorow)
}

```

### Tier II placement rounds
```{r placement-2, results='asis', echo = F}

pp <- matrix(paste0(LETTERS[5:8], rep(2:5, each = 4), ":\n\n\n"), nrow = 4)
xtpp <- xtable(pp)
align(xtpp) <-"|l|X|X|X|X|"
addtorow$pos <- list(0)
addtorow$command <- paste0(" & 29th Place & 33rd Place & 37th Place & 41st Place \\\\\n")

print(xtpp,  type = 'latex', include.colnames = FALSE, include.rownames = TRUE, 
      comment=F, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H", add.to.row = addtorow)

print_placement_schedule(which_bracket = p2948, p2948_rooms)




```

### Tiers II/III Crossover rounds

### Tier III placement rounds

```{r placement-3, results='asis', echo = F}
pp <- matrix(paste0(LETTERS[9:12], rep(2:5, each = 4), ":\n\n\n"), nrow = 4)
xtpp <- xtable(pp)
align(xtpp) <-"|l|X|X|X|X|"
addtorow$pos <- list(0)
addtorow$command <- paste0(" & 53rd Place & 57th Place & 61st Place & 65th place  \\\\\n")
print(xtpp,  type = 'latex', include.colnames = FALSE, include.rownames = TRUE, 
      comment=F, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H", add.to.row = addtorow)

print_placement_schedule(which_bracket = p4971, p4971_rooms)
```

\clearpage

### Tiers II/III Crossover rounds

### Tier IV placement rounds
```{r placement-4, results='asis', echo = F}
pp <- matrix(paste0(LETTERS[13:16], rep(2:6, each = 4), ":\n\n\n"), nrow = 4)
xtpp <- xtable(pp)
align(xtpp) <-"|l|X|X|X|X|X|"
addtorow$pos <- list(0)
addtorow$command <- paste0("& 77th Place & 81st Place & 85th Place & 89th place & 93rd place \\\\\n")
print(xtpp,  type = 'latex', include.colnames = FALSE, include.rownames = TRUE, 
      comment=F, tabular.environment = "tabularx", width = "\\textwidth", table.placement = "H", add.to.row = addtorow)
print_placement_schedule(which_bracket = p7296, p7296_rooms)

```
